Zohmg---a large scale data warehouse for aggregated time-series-based data. [DRAFT]

### 2009-05-05 doc/report/msc-report.tex
doc/report/msc-report.tex: + minor corrections in Data cubes section. + added content to Dimensions section.

A data cube is a conceptual n-dimensional array of values. The values are numerical facts belonging to some dimension. The data cube is also known as a hypercube. In this context, each dimension of the cube corresponds to an attribute of the data in question and each point along the dimensions axis is a value of the corresponding attribute. The mental model of a data cube aids in reasoning about dimensions. Data cubes are traditionally modeled as star schemas in relational database systems.

@@

The dimensions of the data cube are..

>>>>

A data cube is a conceptual n-dimensional array of values. The values are
numerical facts belonging to some dimension. The data cube is also known as a
hypercube, it relates to multidimensional analogues of squares and cubes.
In this context, each dimension of the cube corresponds to an attribute of
the data in question and each point along the dimension's axis is a value of
the corresponding attribute. The mental model of a data cube aids in
reasoning about dimensions. Data cubes are traditionally modeled as star
schemas in relational database systems. \cite{olap_solutions}

@@

The school book example of a data cube is three dimensional where each of
the three dimensions correspond to one of the attributes time, products,
and stores. Adding another attribute adds another dimension to the data
cube, because of the one to one relationship of attributes and dimensions.
